Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

%\subsubsection{PRA Engine Implementation}
Before implementing the solution, we  must first
select the tools that will be used to do the implementation of the PRA Engine. In general, there are many programming languages that can implement solutions of the PRA Engine. However, there is an important need to implement the Kolmogorov-Smirnov (K-S) statistical test which not all programming languages have a support library to do this. There are two programming languages that have libraries for performing K-S tests
which are the Go and Python programming languages. The Go language has the Gonum\footnote{\url{gonum.org}} library which
has a K-S test implementation in the \texttt{KolmogorovSmirnov} function, while the language
Python has the SciPy\footnote{\url{scipy.org}} library which has a K-S test implementation in the \texttt{scipy.stat.ks\textunderscore 2samp} function. From the two languages, we finally decide to choose Python language to implement the solution after successfully parsed the Zipkin trace data with Object-oriented Programming approach based on source code from Zipkin's User Interface application which uses the Javascript language.

\section{Experiment}

>>>>

Before implementing the solution, we  must first
select the tools that will be used to do the implementation of the PRA Engine. In general, there are many programming languages that can implement solutions of the PRA Engine. However, there is an important need to implement the Kolmogorov-Smirnov (K-S) statistical test which not all programming languages have a support library to do this. There are two programming languages that have libraries for performing K-S tests
which are the Go and Python programming languages. The Go language has the Gonum\footnote{\url{gonum.org}} library which
has a K-S test implementation in the \texttt{KolmogorovSmirnov} function, while the language
Python has the SciPy\footnote{\url{scipy.org}} library which has a K-S test implementation in the \texttt{scipy.stat.ks\textunderscore 2samp} function. From the two languages, we finally decide to choose Python language to implement the solution after successfully parsed the Zipkin trace data with Object-oriented Programming approach based on source code from Zipkin's User Interface application which uses the Javascript language.

\section{Experiment}
We test the PRA system in the context of \textbf{Hipster Shop} application hosted by Google Kubernetes Engine, Container Optimized OS (COS), in 3 nodes of n1-standard-2 machine with 2 vCPU and 7.5 GiB RAM.

\subsection{Hipster Shop}
Hipster Shop\footnote{\url{https://github.com/masterraf21/microservices-demo}} is a cloud native microservices demo application
where users can browse items, add them to the
cart, and purchase them. The application contains a 10-tier
microservices application that communicates using gRPC.
Hipster Shop also provides a load generator to simulate user
behaviour. For this experiment purposes, the version of the Hipster Shop which will be used is already instrumented to work with the Zipkin distributed tracing.
